---
title: "Allometry of fitness traits and temperature in hydra - analysis of phenotype data"
author: 'Jácint Tökölyi'
output: html_document
---

# Load and prepare data for graphs and statistics
```{r message=FALSE, warning=FALSE}
library(readxl); library(ggplot2); library(dplyr); library(cowplot)
dat <- read_excel("~/hidra/2023/TempAllometry/ReprAllometry_Temperature.xlsx")
dat$SMgroup<-factor(dat$SMgroup, levels=c("R","E"))
levels(dat$SMgroup)<-c("Reduced","Enlarged")
dat$TEMPgroup<-as.factor(dat$TEMPgroup)
dat$Sex<-factor(ifelse(dat$Strain%in%c("M83/4","C2/7"), "male", "female"),levels=c("male","female"))
dat$Strain <- factor(dat$Strain, levels=c("C2/7", "M83/4", "X11/14", "M26/9/10"))

dat<-dat[which(is.na(dat$Comment)),]

gonads.columns <- grep("[0-9]_[0-9]",names(dat))

dat$Time2gonadogenesis <- as.Date(dat$SexStartDate,format="%Y.%m.%d") - 
  as.Date(dat$CoolingDate,format="%Y.%m.%d")
dat$PairID<-paste(dat$Strain, dat$Set, dat$TEMPgroup, ((dat$Well-1)%%3)+1, sep="_")

dat$maxTestes <- NA
dat$sumEggs <- NA

male.rows <- dat$Strain%in%c("M83/4","C2/7")
female.rows <- dat$Strain%in%c("M26/9/10","X11/14")

dat$maxTestes[male.rows]<-as.numeric(apply(dat[,gonads.columns][male.rows,],1,max,na.rm=T))
dat$sumEggs[female.rows]<-as.numeric(apply(dat[,gonads.columns][female.rows,],1,sum,na.rm=T))
dat$sumEggs[is.na(dat$Time2gonadogenesis)]<-NA
dat$maxTestes[is.na(dat$Time2gonadogenesis)]<-NA

dat$maxTestes[dat$maxTestes == -Inf] <- NA

table(dat$Fate)
dat$Survival<-NA
dat$Survival[dat$Fate%in%c("dead","necrotic")]<-0
dat$Survival[dat$Fate=="regenerated"]<-1
dat$Survival<-as.factor(dat$Survival)

surv <- dat %>% group_by(Sex, Strain, TEMPgroup, SMgroup) %>% count(Survival,.drop=F) %>%
  mutate(prop = n/sum(n))
surv <- as.data.frame(surv)

```

# Prepare graphs
## Reproduction: sexual development time and fecundity
```{r message=FALSE, warning=FALSE}
leg.title <- expression(paste("Temperature (", "\u00B0","C):", sep=""))

## Male sexual development time
male.start <- ggplot(dat[male.rows,], aes(y=Time2gonadogenesis,x=SMgroup,color=TEMPgroup, fill=TEMPgroup,shape=TEMPgroup))+
  facet_wrap(~Strain)+theme_bw()+
  geom_jitter(alpha=0.5,color="black",position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  ylab("Sexual development time") + xlab("Size manipulation group")+labs(shape=leg.title,color=leg.title,fill=leg.title)


## Male fecundity
male.fecundity <- ggplot(dat[male.rows,], aes(y=maxTestes,x=SMgroup,color=TEMPgroup, fill=TEMPgroup,shape=TEMPgroup))+
  facet_wrap(~Strain)+theme_bw()+
  geom_jitter(alpha=0.5,color="black",position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  ylab("No. testes") + xlab("Size manipulation group")+labs(shape=leg.title,color=leg.title,fill=leg.title)

## Female sexual development time
female.start <- ggplot(dat[female.rows,], aes(y=Time2gonadogenesis,x=SMgroup,color=TEMPgroup, fill=TEMPgroup,shape=TEMPgroup))+
  facet_wrap(~Strain)+theme_bw()+
  geom_jitter(alpha=0.5,color="black",position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  ylab("Sexual development time") + xlab("Size manipulation group")+labs(shape=leg.title,color=leg.title,fill=leg.title)

## Female fecundity
female.fecundity <- ggplot(dat[female.rows,], aes(y=sumEggs,x=SMgroup,color=TEMPgroup, fill=TEMPgroup,shape=TEMPgroup))+
  facet_wrap(~Strain)+theme_bw()+
  geom_jitter(alpha=0.5,color="black",position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  ylab("No. eggs") + xlab("Size manipulation group")+labs(shape=leg.title,color=leg.title,fill=leg.title)
```

## Survival

```{r}
male.survival<-ggplot(filter(surv, Sex=="male"&Survival==1&Strain%in%c("C2/7","M83/4")), aes(y=prop, x=SMgroup,color=TEMPgroup,fill=TEMPgroup,group=TEMPgroup,shape=TEMPgroup))+
  geom_col(position = position_dodge2(),alpha=0.5,color="black")+facet_wrap(~Strain,drop=T)+theme_bw()+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.9),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.9),linewidth=1.5)+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  xlab("Size manipulation group")+ylab("Prop. surviving")
  
female.survival<-ggplot(filter(surv, Survival==1&Sex=="female"&Strain%in%c("M26/9/10","X11/14")), aes(y=prop, x=SMgroup,color=TEMPgroup,fill=TEMPgroup,group=TEMPgroup,shape=TEMPgroup))+
  geom_col(position = position_dodge2(),alpha=0.5,color="black")+facet_wrap(~Strain,drop=T)+theme_bw()+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.9),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.9),linewidth=1.5)+
  scale_shape_manual(values=c("12"=24, "8"=21))+
  xlab("Size manipulation group")+ylab("Prop. surviving")


```

## Compensatory growth

```{r}
dat2 <- read_excel("~/hidra/2023/TempAllometry/ReprAllometry_Temperature.xlsx",sheet=2)
dat2$postSize<-dat2$PostArea/(dat2$PostStdmm^2)
dat2$w2Size<-dat2$w2Area/(dat2$w2Stdmm^2)
dat2$TEMPgroup<-as.factor(dat2$TEMPgroup)
dat2$SMgroup<-factor(dat2$SMgroup, levels=c("R","E"))
levels(dat2$SMgroup) <- c("Reduced", "Enlarged")
dat2$PairID<-paste(dat2$Strain, dat2$Set, dat2$TEMPgroup, ((dat2$Well-1)%%3)+1, sep="_")

male.sizechange<-ggplot(dat2[dat2$Strain%in%c("C2/7","M83/4"),], aes(y=w2Size/postSize,color=TEMPgroup, x=SMgroup, fill=TEMPgroup, shape=TEMPgroup))+facet_wrap(~Strain)+theme_bw()+
  geom_jitter(aes(fill=TEMPgroup),colour="black",shape=21,alpha=0.5,size=1.5,
              position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  xlab("Size manipulation group")+ylab("Size change")+labs(shape=leg.title,color=leg.title,fill=leg.title)

female.sizechange<-ggplot(dat2[dat2$Strain%in%c("X11/14","M26/9/10"),], aes(y=w2Size/postSize,color=TEMPgroup, x=SMgroup, fill=TEMPgroup, shape=TEMPgroup))+facet_wrap(~Strain)+theme_bw()+
  geom_jitter(aes(fill=TEMPgroup),colour="black",shape=21,alpha=0.5,size=1.5,
              position=position_jitterdodge())+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar", width=0.5, position=position_dodge(0.5), size=0.7)+
  stat_summary(fun=mean,geom="point",position=position_dodge(0.5),size=4)+
  stat_summary(aes(group=TEMPgroup),fun="mean",geom="line",position=position_dodge(0.5),linewidth=1.5)+
  scale_color_manual(values=c("12"="red","8"="blue"))+
  scale_fill_manual(values=c("12"="red","8"="blue"))+
  xlab("Size manipulation group")+ylab("Size change")+labs(shape=leg.title,color=leg.title,fill=leg.title)

```

## Print graphs
```{r save plots}
library(ggpubr); library(magick)

p1<-"~/hidra/2023/TempAllometry/MS/graph/start.png"
p2<-"~/hidra/2023/TempAllometry/MS/graph/8fok.png"
p3<-"~/hidra/2023/TempAllometry/MS/graph/12fok.png"

p<-ggplot()+xlim(-5,25)+ylim(-1.1,1.1)+draw_image(p1,scale=3,y=-0.5,x=-3)+
  draw_image(p3,scale=3,y=0.25,x=3)+
  draw_image(p2,scale=3,y=-1.25,x=3)+
  theme_bw()+geom_segment(aes(y=0,x=0, yend=0, xend=25), arrow=arrow(length=unit(5,"mm")))+
  annotate("text", label="REPRODUCTION PHASE",x=5, y=0.1,size=4)+
  annotate("text", label="SENESCENCE PHASE",x=19, y=0.1,size=4)+ylab("")+
  geom_segment(aes(x=0,y=0, xend=0, yend=-0.5), color="grey")+
  geom_segment(aes(x=0,y=-0.5, xend=-1, yend=-0.55), color="grey")+
  annotate("text", x=-3,y=-0.6, label=stringr::str_wrap("Week 0: size manipulation",width=20),size=2.5)+
  geom_segment(aes(x=2,y=0, xend=2, yend=-0.05), color="grey")+
  geom_segment(aes(x=2,y=-0.05, xend=2.5, yend=-0.1), color="grey")+
  annotate("text", x=4.5,y=-0.15, label=stringr::str_wrap("Week 2: RNA isolation",width=20),size=2.5)+
  geom_segment(aes(x=8,y=0, xend=8, yend=-0.05), color="grey")+
  annotate("text", x=11,y=-0.15, label=stringr::str_wrap("Weeks 0-22: Quantifying reproductive investment",width=30),
           size=2.5)+
  geom_segment(aes(x=22,y=0.0, xend=22, yend=-0.05), color="grey")+
  annotate("text", x=21, y=-0.15, label=stringr::str_wrap("Week 22: Quantifying survival",width=30),size=2.5)+
  theme(axis.title.x=element_blank(),axis.text.y=element_blank(),axis.ticks.y=element_blank())

g <- as.data.frame(dat[gonads.columns])
gw <- matrix(NA, ncol=22, nrow=nrow(g))
g.dates <-as.Date(paste(ifelse(as.numeric(substring(names(g),1,2))<9, "2023","2022"), names(g),sep="_"), format="%Y_%m_%d")
for(i in 1:nrow(g)){
  for(j in 1:22){
    sel.dates <- which(g.dates > as.Date(dat$CoolingDate,format="%Y.%m.%d")[i]+((j-1)*7+1) & 
                         g.dates <= as.Date(dat$CoolingDate,format="%Y.%m.%d")[i]+7*j)
    if(length(sel.dates)==0) {
      gw[,j][i] <- 0
    } else {
      gw[,j][i] <- ifelse(any(!is.na(g[i,][sel.dates])), 1, 0)
    }
  }
}

g.temp <- cbind(dat[c("TEMPgroup","SMgroup")], gw)
sex.props <- c(apply(g.temp[g.temp$TEMPgroup=="8"&g.temp$SMgroup=="Reduced",][,-(1:2)],2,sum) /     nrow(g.temp[g.temp$TEMPgroup=="8"&g.temp$SMgroup=="Reduced",]),
               apply(g.temp[g.temp$TEMPgroup=="8"&g.temp$SMgroup=="Enlarged",][,-(1:2)],2,sum) /     nrow(g.temp[g.temp$TEMPgroup=="8"&g.temp$SMgroup=="Enlarged",]),
               apply(g.temp[g.temp$TEMPgroup=="12"&g.temp$SMgroup=="Reduced",][,-(1:2)],2,sum) /     nrow(g.temp[g.temp$TEMPgroup=="12"&g.temp$SMgroup=="Reduced",]),
               apply(g.temp[g.temp$TEMPgroup=="12"&g.temp$SMgroup=="Enlarged",][,-(1:2)],2,sum) /     nrow(g.temp[g.temp$TEMPgroup=="12"&g.temp$SMgroup=="Enlarged",]))
g.temp2 <- data.frame(Temperature=rep(c(8,12), each=44),
                      Size=rep(c("R","E","R","E"),each=22),
                      sex.props = sex.props,
                      week=rep(1:22,4))

g8 <- ggplot(g.temp2[g.temp2$Temperature==8,],aes(x=week, y=sex.props,shape=Size,linetype=Size)) + 
  geom_line(color="blue")+geom_point(color="blue")+theme_bw()+xlab("Week")+ylab("Prop.")+
    annotate("text", label=bquote(paste("8", ~degree, "C")),x=20, y=0.625,size=4,color="blue")+
  theme(text = element_text(size = 7),plot.margin=unit(c(0,0,0,0),"mm"))
g12 <- ggplot(g.temp2[g.temp2$Temperature==12,],aes(x=week, y=sex.props,shape=Size,linetype=Size)) + 
  geom_line(color="red")+geom_point(color="red")+theme_bw()+xlab("Week")+ylab("Prop.")+
    annotate("text", label=bquote(paste("12", ~degree, "C")),x=20, y=0.75,size=4,color="red")+
  theme(text = element_text(size = 7),plot.margin=unit(c(0,0,0,0),"mm"))

p2 <- ggdraw()+draw_plot(p)+draw_plot(g8, x=0.38,y=0.065, width=0.6, height=0.38, scale=0.9)+
  draw_plot(g12, x=0.38,y=0.6, width=0.6, height=0.38, scale=0.9)


ragg::agg_tiff(filename="~/hidra/2023/TempAllometry/MS/fig1.tiff",
               width=115,height=174,units="mm",res=300,scaling=0.6)
ggarrange(p2,
  ggarrange(male.fecundity + theme(legend.title.align = 1), 
          male.survival, female.fecundity, female.survival, ncol=2, nrow=2,common.legend = T, labels=c("B","C","D","E")), nrow=2, heights = c(1.25,3), labels=c("A",""))
dev.off()
#ggsave(file="~/hidra/2023/TempAllometry/MS/fig1.tiff",width=174,height=174,units="mm",bg="white")

ggarrange(male.start, female.start, nrow=1, ncol=2, common.legend = T, labels="AUTO")
ggsave(file="~/hidra/2023/TempAllometry/MS/fig_s1.tiff",width=174,units="mm",bg="white")

ggarrange(male.sizechange, female.sizechange, nrow=1, ncol=2, common.legend = T, labels="AUTO")
ggsave(file="~/hidra/2023/TempAllometry/MS/fig_s2.tiff",width=174,units="mm",bg="white")
```

# Statistical analyses

## Male fecundity

```{r fecundity.males}
library(glmmTMB); library(DHARMa); library(bbmle)

# males
hist(dat$maxTestes[male.rows])
mFecundity.males.int <- glmmTMB(maxTestes~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[male.rows,])
mFecundity.males.add <- glmmTMB(maxTestes~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[male.rows,])
anova(mFecundity.males.int, mFecundity.males.add) # Chisq: 17.267 / p < 0.001
summary(mFecundity.males.int)
plot(simulateResiduals(mFecundity.males.int)) # model diagnostics OK
```

## Male survival

```{r survival.males}
mSurvival.males.int <- glmmTMB(Survival~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[male.rows,],family="binomial")
mSurvival.males.add <- glmmTMB(Survival~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[male.rows,],family="binomial")
anova(mSurvival.males.int, mSurvival.males.add) # Chisq: 4.748 / p = 0.029
summary(mSurvival.males.int)
plot(simulateResiduals(mSurvival.males.int)) # model diagnostics OK
```

## Male sexual development time

```{r sexDev.males}
hist(as.numeric(dat$Time2gonadogenesis[male.rows]))
mSexDevTime.males.int <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[male.rows,])
mSexDevTime.males.add <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[male.rows,])
anova(mSexDevTime.males.int, mSexDevTime.males.add) # Chisq: 13.874 / p < 0.001
summary(mSexDevTime.males.int)
plot(simulateResiduals(mFecundity.males.int)) # model diagnostics OK
```

## Male compensatory growth

```{r compGrowth.males}
hist(dat2$w2Size[dat2$Strain%in%c("C2/7","M83/4")]/dat2$postSize[dat2$Strain%in%c("C2/7","M83/4")],breaks=50)
hist(log(dat2$w2Size[dat2$Strain%in%c("C2/7","M83/4")]/dat2$postSize[dat2$Strain%in%c("C2/7","M83/4")]),breaks=50)
mSizeChange.males.int <- glmmTMB(log(w2Size/postSize)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat2[dat2$Strain%in%c("C2/7","M83/4"),])
mSizeChange.males.add <- glmmTMB(log(w2Size/postSize)~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat2[dat2$Strain%in%c("C2/7","M83/4"),])
anova(mSizeChange.males.int, mSizeChange.males.add) # Chisq = 0.788 / p = 0.374
plot(simulateResiduals(mSizeChange.males.int)) # model diagnostics OK
```

## Female fecundity

```{r fecundity.females}
#females
hist(dat$sumEggs[female.rows])
mFecundity.females.int.gaussian <- glmmTMB(sumEggs~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="gaussian")
mFecundity.females.int.poisson <- glmmTMB(sumEggs~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="poisson")
mFecundity.females.int.negbin1 <- glmmTMB(sumEggs~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="nbinom1")
mFecundity.females.int.negbin2 <- glmmTMB(sumEggs~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="nbinom2")
AICctab(mFecundity.females.int.gaussian, mFecundity.females.int.poisson, mFecundity.females.int.negbin1, mFecundity.females.int.negbin2) ## nbinom2 model selected best

mFecundity.females.add <- glmmTMB(sumEggs~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[female.rows,],family="nbinom2")
anova(mFecundity.females.int.negbin2, mFecundity.females.add) # Chisq: 7.607 / p = 0.006
summary(mFecundity.females.int.negbin2)
plot(simulateResiduals(mFecundity.females.int.negbin2)) # model diagnostics OK
```

## Female survival

```{r survival.females}
mSurvival.females.int <- glmmTMB(Survival~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,],family="binomial")
mSurvival.females.add <- glmmTMB(Survival~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[female.rows,],family="binomial")
anova(mSurvival.females.int, mSurvival.females.add) # Chisq: 0.998 / p = 0.318
plot(simulateResiduals(mSurvival.females.int)) # model diagnostics OK
```

## Female sexual development time

```{r sexDev.females}
hist(as.numeric(dat$Time2gonadogenesis[female.rows]),breaks=100)
mSexDevTime.females.int.gaussian <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="gaussian")
mSexDevTime.females.int.poisson <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="poisson")
mSexDevTime.females.int.nbinom1 <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="nbinom1")
mSexDevTime.females.int.nbinom2 <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat[female.rows,], family="nbinom2")
AICtab(mSexDevTime.females.int.gaussian, mSexDevTime.females.int.poisson, mSexDevTime.females.int.nbinom1, mSexDevTime.females.int.nbinom2) ## the nbinom1 and nbinom2 models did not converge; gaussian is better over poisson
plot(simulateResiduals(mFecundity.females.int.gaussian)) # model diagnostics not OK, but not too bad

mSexDevTime.females.add.gaussian <- glmmTMB(as.numeric(Time2gonadogenesis)~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat[female.rows,],family="gaussian")
anova(mSexDevTime.females.int.gaussian, mSexDevTime.females.add.gaussian) # Chisq: 14.965 / p < 0.001
```

## Female compensatory growh

```{r compGrowth.females}
hist(dat2$w2Size[dat2$Strain%in%c("X11/14","M26/9/10")]/dat2$postSize[dat2$Strain%in%c("X11/14","M26/9/10")],breaks=50)
hist(log(dat2$w2Size[dat2$Strain%in%c("X11/14","M26/9/10")]/dat2$postSize[dat2$Strain%in%c("X11/14","M26/9/10")]),breaks=50)
mSizeChange.females.int <- glmmTMB(log(w2Size/postSize)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat2[dat2$Strain%in%c("X11/14","M26/9/10"),])
mSizeChange.females.add <- glmmTMB(log(w2Size/postSize)~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat2[dat2$Strain%in%c("X11/14","M26/9/10"),])
anova(mSizeChange.females.int, mSizeChange.females.add) # Chisq = 6.945 / p = 0.008
plot(simulateResiduals(mSizeChange.females.int))
```

## Compensatory growth sexes combined

```{r compGrowth.combined}
## sexes combined

mSizeChange.int <- glmmTMB(log(w2Size/postSize)~SMgroup*TEMPgroup+Strain+(1|PairID), data=dat2)
mSizeChange.add <- glmmTMB(log(w2Size/postSize)~SMgroup+TEMPgroup+Strain+(1|PairID), data=dat2)
anova(mSizeChange.int, mSizeChange.add) # Chisq = 5.176 / p = 0.023
plot(simulateResiduals(mSizeChange.int))

```